### 2019-02-15 sections/introduction.tex
improve intro

@@

Many applications these days are developed to support workflows in institutions and businesses.
Take for example expenses declarations, order processing, and emergency management.
Not all of these workflows happen inside organisations.
Some occur on the boundary with customers, like flight bookings or tax returns.
What they all have in common is,
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).

Task-oriented programming (\TOP) is a programming paradigm which searches for the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting this workflow.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
The paradigm takes collaboration patterns as the base of modelling
and anticipates on user's need to interact and share information.
A language that supports \TOP should allow to specify tasks from real world scenarios,
and be able to generate multi-user web applications to support these scenarios.
By choosing the right level of abstraction,
\TOP focusses on creating workflow specifications,
while automatically providing common development duties like designing \GUI\ s, connecting to databases, and communicating between servers and client.

>>>>

\subsection{Tasks}

Many applications these days are developed to support workflows in institutions and businesses.
Take for example expense declarations, order processing, and emergency management.
Some of these workflows occur on the boundary between organisations and customers,
like flight bookings or tax returns.
What they all have in common is,
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).

@@

Task-oriented programming (\TOP) is a programming paradigm which searches for the sweet spot between faithful modelling workflows
and rapid prototyping of multi-user web applications supporting these workflows.
% Task-oriented programming (\TOP) is a programming paradigm to support these ways of working.
\TOP focusses on modelling collaboration patterns.
This gives rise to user's need to interact and share information.
Next to that, \TOP automatically provides solutions to common development jobs like designing \GUI\ s, connecting to databases, and communicating between servers and clients.
Therefore,
a language that supports \TOP should choose the right level of abstraction to support two things.
First, it should allow to specify tasks from real world scenarios.
Second, it should be able to generate multi-user web applications to support these scenarios.

\subsection{Utilisation}
